---
title: My dynamic report
output: html_fragment
---

<meta charset="UTF-8">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## Outfit of the Day (OOTD) Survey Analysis

This report analyses observational data on people's outfits, focusing on style and colour patterns.


```{r}

library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQwa0KzvNwSWYPl_38eGjV2nEKcNmP01lBnoxPvLINw8vjhkAhWC7uwwf1OPoGCxLVVDyxESMxic4nO/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp = Timestamp,
    main_color = `What is the main color of your OOTD?
你的OOTD的主要颜色是什么？`,
    style = `What is the overall style of your OOTD?
你的OOTD的整体风格是什么？`,
    num_colors = `How many colors are there in your OOTD?
你的OOTD里有多少种颜色？`
  )


```

```{r}
mean_colors <- mean(latest_data$num_colors, na.rm = TRUE)

max_colors <- max(latest_data$num_colors, na.rm = TRUE)

min_colors <- min(latest_data$num_colors, na.rm = TRUE)

total_observation <- nrow(latest_data)

```
The average number of colors in an outfit across all observations is **`r round(mean_colors, 2)`**.

The maximum number of colors observed in one suit is **`r max_colors`**.

The minimum number of colors observed in one suit is **`r min_colors`**.

The total number of observations in the dataset is **`r total_observation`**.


```{r}
# plot 1
ggplot(latest_data, aes(x = style)) + 
  geom_bar() +
  labs(
    title = "Distribution of Outfit Styles",
    x = "Style",
    y = "Count"
  )

# plot 2
ggplot(latest_data, aes(x = main_color)) +
  geom_bar() +
  labs(
    title = "Distribution of Main Colors",
    x = "Main Color",
    y = "Count"
  )

```

